The \dealii Library, Version 9.7

### 2025-07-30 9.7/paper.tex
Update MF acknowledgments.

M.~Fehling was also partially supported by the ERC-CZ grant LL2105
CONTACT, funded by the Czech Ministry of Education, Youth and Sports.

>>>>

M.~Fehling was partially supported by the ERC-CZ grant LL2105 CONTACT,
funded by the Czech Ministry of Education, Youth and Sports. He was also
partially supported by the Charles University Research Centre Program No.\@ UNCE/24/SCI/005.
